---
title: "Stream Visualisation"
author: "Grace Heron"
date: "29/07/2020"
output: 
    github_document:
        html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Reference for some nice streams (subjective). Everything works for R4.0.2 and proj6. Important packages:

```{r pkg, message = FALSE}
library(rgdal)
library(raster)
library(tidyverse)
library(ggspatial)
library(ggrepel)
library(SSN)
```


## Yankee-Fork Streams

Yankee-Fork, USA streams with sites, prediction sites and watershed layers.

```{r yf1, message = FALSE}
sites <- readOGR("gisdata/yankeefork","sites")
preds <- readOGR("gisdata/yankeefork", "preds")
watershed <- readOGR("gisdata/yankeefork/watershed.shp", "watershed")
streams <- readOGR("gisdata/yankeefork","streams")
```

### Simple Stream Network

Stream network where the width is proportional to some downstream accumulative value.  

```{r}
ggplot() +
  layer_spatial(streams, 
                aes(size = afvArea), 
                colour = "lightskyblue") +
  coord_sf() + 
  scale_size(range = c(0, 2), guide = FALSE) +
  theme_classic()
```


### Watershed study area with observation sites

Getting slightly fancy. Now add in a watershed and observation sites. Also an annotation arrow for flavour.

```{r}
ggplot() +
  layer_spatial(watershed, fill = "gray60", alpha = 0.5, colour = "gray40") +
  layer_spatial(streams, aes(size = afvArea), colour = "gray50") +
  layer_spatial(sites, colour = "coral", pch = 1, cex = 2, show.legend = TRUE)+
  coord_sf() + 
  labs(x = "Longitude", y = "Latitude") + 
  annotation_north_arrow(height = unit(0.3, "in"),
                         width = unit(0.3, "in"), # GRID NORTH? OR TRUE NORTH?
                         which_north = "grid", 
                         location = "bl") +
  scale_size(range = c(0, 2), guide = FALSE) +
  scale_shape_manual(values=c(25, 24)) + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        axis.text.y = element_text())
```

## Maleny Streams 

